Data Management \\ and LSST Special Programs

### 2021-11-27 DMTN-065.tex
all jira references removed now

DMS-REQ-0320 states that "it shall be possible for special programs to trigger their own data processing recipes". A header keyword identifying an image as related to a Special Program would be sufficient to send it to a dedicated processing pipeline, and would satisfy this requirement. JIRA ticket DM-12576 is currently open to make sure that this happens.

@@

In cases where the science goals of a Special Program require specialized algorithms and cannot be achieved by reconfiguring DM's software, then user-generated pipelines will be needed. Towards this end, LSST DM is making all of its software open-source, and preparing the Science Platform (\citeds{LSE-319}), through which users can access the tools and computational resources to assemble data processing pipelines to achieve their science goals (whether related to Special Programs data or not). During Operations, there will be a method for the system to allocation processing resources in the case of over-subscription. JIRA ticket DM-12577 is currently open to inspire an investigation of whether additional Science Platform capabilities are needed to enable user-driven processing of Special Programs data.

@@

It is furthermore expected that, over time, some user-designed pipelines might become ``adopted", installed and operated (and change controlled) by the LSST Operations team. For both adopted and user-run code, whether they are for Special Programs or WFD survey data, the LSST DM team will encourage and facilitate data product databases that are built with the same schema as -- and can easily be joined with -- the tables of the Prompt and DRP data products. An alternative option to ``adopted" code is ``adopted" data products: situations in which user-generated code is run externally, a data catalog is returned to LSST to be ingested, verified, and made public. JIRA ticket DM-12578 is currently open to consider the staffing needs and process for adopting user-generated code or products; this issue is not necessarily limited to Special Programs.

@@

Step 4. Reconfigured Processing Pipelines and Separate Data Products. \\
The required data products for this science goal can be met by reconfiguring the DM pipelines. First, a template image for the field will be made using DM stacking algorithms. On nights when this DDF is observed, at the end of the sequence of observations, DM algorithms are used to create a nightly deep stack, PSF-match it with the template, create a deep difference image, run source detection on the differences, and create separate databases of \texttt{DIAObject}, \texttt{DIASource}, and \texttt{Object} that are unique to this DDF. The LSST codes for alert packet and transport could be used to distribute the detected objects e.g., to the same brokers that receive the Alert Stream, or alternative destinations. However, these packets would not be distributed via the LSST {\tt Alert Stream}, and would need to be identified as, e.g., DDF Alerts. Note that JIRA ticket DM-12585 is currently open to investigate whether or not the internal real/bogus routine be able to run on a nightly CoAdd of deep drilling difference images.

>>>>

DMS-REQ-0320 states that "it shall be possible for special programs to trigger their own data processing recipes".
A header keyword identifying an image as related to a Special Program will be included (e.g., the survey name), and that will be sufficient to send it to a dedicated processing pipeline.

@@

In cases where the science goals of a Special Program require specialized algorithms and cannot be achieved by reconfiguring DM's software, then user-generated pipelines will be needed.
Towards this end, LSST DM is making all of its software open-source, and preparing the Science Platform (\citeds{LSE-319}), through which users can access the tools and computational resources to assemble data processing pipelines to achieve their science goals (whether related to Special Programs data or not).
During Operations, there will be a method for the system to allocation processing resources in the case of over-subscription.

@@

It is furthermore expected that, over time, some user-designed pipelines might become ``adopted", installed and operated (and change controlled) by the LSST Operations team.
For both adopted and user-run code, whether they are for Special Programs or WFD survey data, the LSST DM team will encourage and facilitate data product databases that are built with the same schema as -- and can easily be joined with -- the tables of the Prompt and DRP data products.
An alternative option to ``adopted" code is ``adopted" data products: situations in which user-generated code is run externally, a data catalog is returned to LSST to be ingested, verified, and made public.

@@

Step 4. Reconfigured Processing Pipelines and Separate Data Products. \\
The required data products for this science goal can be met by reconfiguring the DM pipelines. First, a template image for the field will be made using DM stacking algorithms. On nights when this DDF is observed, at the end of the sequence of observations, DM algorithms are used to create a nightly deep stack, PSF-match it with the template, create a deep difference image, run source detection on the differences, and create separate databases of \texttt{DIAObject}, \texttt{DIASource}, and \texttt{Object} that are unique to this DDF. The LSST codes for alert packet and transport could be used to distribute the detected objects e.g., to the same brokers that receive the Alert Stream, or alternative destinations. However, these packets would not be distributed via the LSST {\tt Alert Stream}, and would need to be identified as, e.g., DDF Alerts.
